Unsupervised Detection and Tracking of Arbitrary Objects with Dependent Dirichlet Process Mixtures

### 2012-02-08 ltx/paper_short_2.tex
a few more edits. as before, main file is: paper_short_2.tex

A basic set of observations that can be extracted from video are three-dimensional points $\bold{x} = ( x_{1}, x_{2}, t ) \in \mathbb{R}^{2} \times \mathbb{Z}_{+}$, where $x_{1}$ and $x_{2}$ are the two spatial locations of a pixel. Extraction procedures, such as those discussed in Section~\ref{sec:introduction}, are used to isolate pixels lying in the regions of a video that represent objects. For implementation in experiments (Section~\ref{sec:experiments}), we desire an extraction procedure that is as unsophisticated as possible, both to gauge the robustness of this method on potentially noisy extraction data and to ensure that the procedure is applicable to a wide range of videos. Accordingly, we carry out a method called ``frame differencing'' for all experiments, which locates regions within video frames that contain motion by recording the positions of pixels exhibiting large enough differences in intensity or value between succesive frames. Frame differencing is unsophisticated, computationally inexpensive, able to be applied to a wide range of static, single-camera videos (note that videos used in all experiments were stationary; moving-camera videos require extraction methods useful for non-stationary video, such as \willie{cite cite cite}). Examples of pixel location data extracted via frame differencing are shown in Fig.~\ref{fig:img_and_framediff}(a-j).

@@

We have not found an easily justifiable way to choose parameters. For the appearance and movement parameters, samples were drawn given a range of parameter values, and those that yielded samples similar in appearance to the experimental data were kept (a technique also performed in \cite{gasthaus_thesis}). The parameters chosen for use in experiments (Section~\ref{sec:experiments}) were accepted based on the fact that they yielded reasonable results. Additionally, a sensitivity analysis was carried out for the concentration and deletion parameters ($\alpha$ and $\rho$), where a range of values for both were chosen, and inference performed for each; results of this analysis are discussion in Section~\ref{sec:sensitivityanalysis}.

@@

Bayesian inference algorithms, which infer distributions over latent model parameters, are used to get detection and tracking results. A variety of methods previously developed for statistical inference can be applied to the generative model defined in Sections~\ref{sec:} and \ref{sec}.

 we separate presentations of model and inference so that multiple inference methods, each with its own benefits in terms of precision and speed, can be formulated as independent algorithms for detection and tracking. This section provides background on the two inference algorithms implemented in this study, which are both used to perform Bayesian inference on the model described in Section~\ref{sec:modelspec}. The first is a type of Markov Chain Monte Carlo (MCMC) batch inference, which uses Gibbs sampling to generate samples from the posterior distribution of the model. The second is a type of Sequential Monte Carlo (SMC) inference, also known as a particle filter, which also generates samples from the posterior distribution of the model, but in a sequential manner that makes use of the time-dependent nature of the data.

@@

\subsubsection{Sampling Deletion Variables $d_{i,t}$}
Computing a value proportional to the posterior distribution for each possible value that a given deletion variable may take on may be accomplished in a manner similar to how samples from the posterior distribution of the assignment variables $c_{i,t}$ are gained in Section~\ref{sec:sample_assignments}; however, this may be computationally expensive due to the large number of possible deletion times. To remedy this, the M-H algorithm may again be used to sample from the posterior, where the prior distribution for the deletion times can be used to propose new samples $d_{i,t}^{*}$. As the ``lifetime'' $l_{i,t}$ of each assignment can be shown to be geometrically distributed, we can propose a new deletion time sample with
\begin{align}
\begin{split}
l_{i,t}  &\sim  \text{Geo}(\rho)  \\
d_{i,t}^{*}  &= l_{i,t} + t + 1
\end{split}
\end{align}
and accept or reject this sample using the standard M-H acceptance ratio.

%%%%%
% need to include the "standard M-H acceptance ratio"
%%%%%

>>>>

A basic set of observations that can be extracted from video are three-dimensional points $\bold{x} = ( x_{1}, x_{2}, t ) \in \mathbb{R}^{2} \times \mathbb{Z}_{+}$, where $x_{1}$ and $x_{2}$ are the two spatial locations of a pixel. Extraction procedures, such as those discussed in Section~\ref{sec:introduction}, are used to isolate pixels lying in the regions of a video that represent objects. For implementation in experiments (Section~\ref{sec:experiments}), we desire an extraction procedure that is as unsophisticated as possible, both to gauge the robustness of this method on potentially noisy extraction data and to ensure that the procedure is applicable to a wide range of videos. Accordingly, we carry out a method called ``frame differencing'' for all experiments, which locates regions within video frames that contain motion by recording the positions of pixels exhibiting large enough differences in intensity or value between succesive frames. Frame differencing is unsophisticated, computationally inexpensive, able to be applied to a wide range of static, single-camera videos (note that videos used in all experiments were stationary; moving-camera videos require extraction methods useful for non-stationary video, such as \cite{chien2002efficient, zhang2007moving}). Examples of pixel location data extracted via frame differencing are shown in Fig.~\ref{fig:img_and_framediff}(a-j).

@@

The parameters chosen for use in experiments (Section~\ref{sec:experiments}) were accepted based on the fact that they yielded reasonable results. Additionally, a sensitivity analysis was carried out for the concentration and deletion parameters ($\alpha$ and $\rho$), where a range of values for both were chosen, and inference performed for each; results of this analysis are discussion in Section~\ref{sec:sensitivityanalysis}.

@@

Bayesian inference algorithms, which infer distributions over latent model parameters, are used to get detection and tracking results. A variety of methods previously developed for statistical inference can be applied to the generative model defined in Sections~\ref{sec:gpuddpm} and \ref{sec:modelspecification}. We've separated descriptions of the model and inference algorithms so that multiple inference methods, each with its own benefits in terms of precision and speed, can be formulated as independent algorithms for detection and tracking. This section provides background on the two Bayesian inference algorithms implemented in this study. The first is a type of Markov Chain Monte Carlo (MCMC) batch inference, which uses Gibbs sampling to generate samples from the posterior distribution of the model. The second is a type of Sequential Monte Carlo (SMC) inference, also known as a particle filter, which also generates samples from the posterior distribution of the model, but in a sequential manner that makes use of the time-dependent nature of the data.

@@

\subsubsection{Sampling Deletion Variables $d_{i,t}$}
Computing a value proportional to the posterior distribution for each possible value that a given deletion variable may take on may be accomplished in a manner similar to how samples from the posterior distribution of the assignment variables $c_{i,t}$ are gained in Section~\ref{sec:sample_assignments}; however, this may be computationally expensive due to the large number of possible deletion times. To remedy this, the M-H algorithm may again be used to sample from the posterior, where the prior distribution for the deletion times can be used to propose new samples $d_{i,t}^{*}$. As the ``lifetime'' $l_{i,t}$ of each assignment can be shown to be geometrically distributed, we can propose a new deletion time sample with
\begin{align}
\begin{split}
l_{i,t}  &\sim  \text{Geo}(\rho)  \\
d_{i,t}^{*}  &= l_{i,t} + t + 1
\end{split}
\end{align}
and accept or reject this sample using the standard M-H acceptance ratio.
%%%%%
% need to include the "standard M-H acceptance ratio"
%%%%%
